%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Data Scientist\newline Data Scientist} % Job title
    {Capital One Bank (Canada Branch)} % Organization
    {Toronto, Ontario, Canada} % Location
    {Jun. 2017 - Present\newline Sep. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a core risk model and its end-to-end scoring pipeline for customer management.}\\
        \begin{cvitems}
          \item {The whole process involved sample selection, data pull, data cleaning and validation, feature creation and selection, model build and validation, model deployment, and documentation.}
          \item {Used SQL, SAS and Tableau for data cleaning and validation, and R for feature selection and model build}
          \item {Deployed the model on our internal scoring platform as a Python package}\\
        \end{cvitems}
        \item {Wrote Python package to programmatically generate complex features from raw data.}
        \item {Built Monte Carlo simulation in Python for call volume prediction.}
        \item {Continuous monitoring of all internal statistical models.}\\
        \begin{cvitems}
          \item {Monitoring the distribution shift in model inputs and the performance of model outputs; detect and resolve model failures.}
          \item {Automated the process to generate monitoring reports.}\\
        \end{cvitems}
      \end{cvitems}
    }

\end{cventries}
