%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {AI Squared Forum} % Job title
    {Bone X-Ray Deep Learning Competition from Stanford ML Group} % Organization
    {Toronto, Ontario, Canada} % Location
    {Jun 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The challenge is to determine whether the bones presented in the x-ray pictures are normal. There are $\sim$38K images from $\sim$15K different studies.}
        \item {Led a team to learn computer vision techniques by participating in the challenge.}
        \item {Set up data pre-processing pipelines, training pipelines and designed evaluation metrics with Keras. Achieved good result with an ensemble of DenseNet trained with Adam using cyclical learning rate.}
        \item \href{https://github.com/DeepMachineLearning/mura-team2}{\textbf{Github}: DeepMachineLearning/mura-team2}
      \end{cvitems}
    }

\end{cventries}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Exploratory Project} % Job title
    {Wasserstien GAN} % Organization
    {Toronto, Ontario, Canada} % Location
    {Jan 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learned TensorFlow with exploratory project.}
        \item {Explored autoencoder and Wasserstein GAN (WGAN) on MNIST data. Implemented Conditional WGAN.}
        \item \href{https://github.com/r-luo/tensorflow-try}{\textbf{Github}: r-luo/tensorflow-try}
      \end{cvitems}
    }

\end{cventries}

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Course Project} % Job title
    {STA490: Statistical Consultation, University of Toronto} % Organization
    {Toronto, Ontario, Canada} % Location
    {Oct. 2014 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated as a group with a student on her research project in Ecology and Evolutionary Biology. The project inspects the behavioural patterns of different groups of golden headed lion tamarins (GHLT) in the presence of various predictors.}\\ 
        \begin{cvitems} 
          \item {Applied various clustering methods on 10 years of field observational data ($\sim$140K observations) to group predictors based on the categories of their preys.}
          \item {Used Markov Chain to model GHLT behaviour changes in time. Wrote R program to estimate the transition matrix, stationary distribution and confidence intervals.}\\
        \end{cvitems}
      \end{cvitems}
    }

\end{cventries}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Analyst | Quantitative Analysis Team} % Affiliation/role
    {Hart House Investment Club, University of Toronto} % Organization/group
    {Toronto, Ontario, Canada} % Location
    {Sep. 2014 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Used other teams’ analyses as prior along with historical data to produce posterior distribution of stock prices, then hedge the portfolio based on the results with sector ETFs.}
      \end{cvitems}
    }
\end{cventries}
