%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------


\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Course Project} % Job title
    {CS7642: Reinforcement Learning, Georga Institute of Technology} % Organization
    {Toronto, Ontario, Canada} % Location
    {Mar 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a deep reinforcement agent to solve the OpenAI Gym Lunar Lander environment and successfully solved the environment by achieving a score greater than 200 over 100 trials.}
        \item {Utilized double deep Q network with experience replay and explored the effect of different hyperparameters on training.}
        \item {Source code and project report available upon request.}
      \end{cvitems}
    }

\end{cventries}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {AI Squared Forum} % Job title
    {Bone X-Ray Deep Learning Competition from Stanford ML Group} % Organization
    {Toronto, Ontario, Canada} % Location
    {Jun 2018 - Oct 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The challenge is to determine whether the bones presented in the x-ray pictures are normal. There are $\sim$38K images from $\sim$15K different studies.}
        \item {Led a team to learn basic computer vision techniques by participating in the challenge.}
        \item {Set up data pre-processing pipelines, training pipelines and designed evaluation metrics with Keras. Achieved result on par with the benchmark model with an ensemble of DenseNet trained with Adam using cyclical learning rate.}
        \item \href{https://github.com/DeepMachineLearning/mura-team2}{\textbf{Github}: DeepMachineLearning/mura-team2}
      \end{cvitems}
    }

\end{cventries}
